\documentclass[dissertation.tex]{subfiles}
\begin{document}

{\large
\begin{tabular}{ll}
Name:               & \bf Andrius Grabauskas                    \\
College:            & \bf Robinson College                      \\
Project Title:      & \bf Measuring mutual information in Neural Networks \\
Examination:        & \bf Computer Science Tripos -- Part II, July 2001  \\
Word Count:         & \bf 6208\footnotemark[1] \\
Line Count:         & \bf 1303\footnotemark[2] \\
Project Originator: & Dr.\ Damon Wischik                  \\
Supervisor:         & Prof.\ Alan Mycroft                 \\ 
\end{tabular}
}
\footnotetext[1]{This word count was computed
by \texttt{detex *.tex | tr -cd '0-9A-Za-z $\tt\backslash$n' | wc -w}
}
\footnotetext[2]{This line count was computed 
by \texttt{wc -l **/*.py}
}
\stepcounter{footnote}


\section*{Original Aims of the Project}

The aim of the project was to reproduce Tishby's results, and see if they
robust. Explore ideas that Tishby presented in his paper, such as: 
\begin{itemize}
  \item{
      Compression in Neural Networks -- if a Neural Network can lose
      information, if so how it happens what assumptions are made.
    }
  \item{
      Compression Phase in Neural Networks -- Tishby claims that the reason why
      Neural Networks generalize is because they learn how to compress the input
      representation. It would be interesting to explore if his claims hold any
      water.
    }
\end{itemize}

\section*{Work Completed}

Reproduced Tishby's code and experiments. Extended the code to reproduce
experiments conducted by Saxe. Extended the code to explore A Novel Mutual
Information Estimation Idea. Produced code to plot the Information Plane as well
as visualize the process in a video format.

\section*{Special Difficulties}
\begin{itemize}
  \item{
      Getting Mutual Information Estimation to work was tricky and took a big
      chunk of time. Had to abandon some methods as they were too complex and
      required too much time.
    }
  \item{
      Wasn't able to conduct all the experiments I wanted -- Such as testing
      different Datasets. The code supports such experiments, but I wasn't able
      to get them done in time.
    }
\end{itemize}

\newpage

\end{document}
